---
title: Aspects of Project Management
---

{{< include _setup.qmd >}}

## How frequently is this aspect of project management a necessary part of your typical project workflow?

```{r frequency}
#| echo: false
#| warning: false
plot_props("frequency", "Frequency")
```

## In your view, how significant are the consequences for project outcomes when this aspect of project management is not addressed?

```{r consequences}
#| echo: false
#| warning: false
plot_props("consequences", "Significance")
```

**Critical** - Total failure; primary goals become impossible to achieve.  
**Major** - Severe disruptions requiring significant rework or loss of features.  
**Moderate** - Noticeable issues requiring specific fixes or causing minor delays.  
**Minor** - Small inconveniences easily managed without impacting the final outcome.  
**Negligible** - Barely any impact; no measurable effect on the project.  

## When this aspect arises, which best describes your typical approach?

```{r approach}
#| echo: false
#| warning: false
plot_props("approach", "Approach")
```

**Structured** - I use specific strategies or frameworks.  
**Ad-hoc** - I handle it informally on a case-by-case basis without specific strategies.  
**Not Managed** - I do not currently address or manage this aspect.  

## Have you used a specific, structured strategy for this aspect in the past?

If you responded "Ad-hoc" or ""Not Managed"

```{r prev-use}
#| echo: false
#| warning: false

plot_props("prev_use", "Used a structured strategy previously")
```

## Would you be open to adopting a structured strategy/approach for this in the future?

If you responded "Ad-hoc" or "Not Managed"

```{r adopting}
#| echo: false
#| warning: false

plot_props("adopting", "Open to adopting a structured strategy")
```
